---
title: "flight_delay"
author: "Balaji Ramkumar and Amish Satish"
date: "14/10/2017"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

#Insatlling the required packages
```{r}
library(tidyverse)

library(nycflights13)

library(caret)
```

#Extracting flight and weather information
```{r}

flights1 <- nycflights13::flights

weather1 <- nycflights13::weather
```


The we create a data frame which requires the required information for testing. Since the data frame is large we are taking a part of it. Since the data frame is too large for analysis we take a small part of the data frame so that it will be easy for us to make the analysis.

#Taking a part of the data
```{r, eval=FALSE, include=TRUE}
datfram1 <- datfram1 %>%
  
  sample_frac(.1)
```


Using dplye we select the coloumns which are required in the data frame and we just keep that.

#Deleting unwanted columns
```{r, eval=FALSE, include=TRUE}

datfram1 <- datfram1 %>%
  
  dplyr::select(-c(sched_dep_time, carrier, flight, tailnum, dest,
                   
                   minute, time_hour, wind_gust))
```

#Creating a Training data
```{r, eval=FALSE, include=TRUE}

traindat<- createDataPartition(y = datfram1$arr_delay, 
                                
                                p = .8, 
                                
                                list = FALSE)



training <- datfram1[traindat, ]

tmp <- datfram1[-traindat, ]
```

The we create a testing data and samples. 

#Creationof models
```{r, eval=FALSE, include=TRUE}
#model1

start <- Sys.time()

lmr_fit1 <- train(arr_delay ~ .,
                  
                  data = training,
                  
                  method = "ridge",
                  
                  trControl = resamp,
                  
                  preProc = "scale")

end <- Sys.time()

end-start

#model2

lmr_fit2 <- train(formula_short,
                  
                  data = training,
                  
                  method = "ridge",
                  
                  trControl = resamp,
                  
                  preProc = "scale")
```

Once the models are created, they are used for prdeicting and evaluation.

#Predicting
```{r, eval=FALSE, include=TRUE}

lmr_class1 <- predict(lmr_fit1, newdata = validate)

lmr_class2 <- predict(lmr_fit2, newdata = validate)


```


The next step is to determine which is the best and capable model.
```{r, eval=FALSE, include=TRUE}


resamp <- resamples(list(rreg_all_vars = lmr_fit1,
                         
                         rreg_high_cor = lmr_fit2))
```


From this it is shown that the model with lambda = 1e-04 is the best model.




